Wigglyhedra

### 2024-05-24 draft/wigglyhedra.tex
minor changes

@@

@@

>>>>

\vincent{Asilata has an alternative description of the flip...}

@@

\vincent{The incompatibility degree is the number of ``close'' minors of the form~$\begin{bmatrix} 1 & -1 \\ -1 & 1 \end{bmatrix}$ or~$\begin{bmatrix} -1 & 1 \\ 1 & -1 \end{bmatrix}$ in the matrix obtained from the two $\b{g}$-vectors of the wiggly arcs.}

@@

\section*{Acknowledgements}

This work started during the \emph{Winterbraids XIII: School on low dimensional topology, braid groups and interactions}. We are grateful to the organizers Bérénice Delcroix-Oger, Peter Feller, Vincent Florens, Hoel Queffelec for this fruitful event.
